\Title

### 2016-08-17 manuscript/manuscript.tex
Rename our method section
Make it clearer where the speed gain comes from (not calculating A all
the time).

Fixes #31

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Regularized Bott's method in spherical coordinates}

We propose a regularized version of Bott's method to invert gravity data for
estimating the depth of the Moho in spherical coordinates.
To adapt Bott's method to spherical coordinates,
we replace the right-rectangular prisms in the forward modeling
($\mathbf{d}(\mathbf{p}^k)$ in Eq.~\ref{eq:bott})
with tesseroids.
The tesseroid forward modeling uses the adaptive discretization algorithm
of \citet{uieda2016} to achieve accurate results.
Furthermore, our formulation maintains the regularized solution
for the Gauss-Newton method (Eq.~\ref{eq:gaussnewton-regul})
but replaces the full Jacobian matrix with the Bouguer plate approximation
(Eq.~\ref{eq:bott-gaussnewton}).
Here, the Jacobian matrix is a diagonal matrix whose elements are invariant
along successive iterations.
Using this approximation eliminates the cost of computing and storing
the full Jacobian matrix $\mathbf{A}^k$ at each iteration
(Eq.~\ref{eq:jacobian}).
Matrix arithmetic operations can be performed efficiently by taking advantage
of the sparse nature of matrices $\mathbf{A}$ and $\mathbf{R}$
(respectively, Eq.~\ref{eq:bott-gaussnewton} and \ref{eq:regul}).
The same is true for solving the equation system in the Gauss-Newton method
(Eq.~\ref{eq:gaussnewton-regul}).
However, the computational cost of forward modeling is still present.
Particularly, forward modeling using tesseroids is more computationally
intensive than using right-rectangular prisms
because of the numerical integration and adaptive discretization
\citep{uieda2016}.
We show later in this article that sparse matrix multiplications and solving
the sparse linear system in Eq.~\ref{eq:gaussnewton-regul} account for less
than 0.1\% of the computation time required for a single inversion.
Hence, by employing the use of sparse matrices, our formulation retains the
efficiency of Bott's method while stabilizing the solution through the well
established formalism of Tikhonov regularization.

@@

We have developed a computationally efficient gravity inversion method in
spherical coordinates.
Our method extends the Gauss-Newton formulation of Bott's method
\citep{silva2014} to use tesseroids as model elements and smoothness
regularization.
We retain the computational efficiency of Bott's method by taking advantage of
the sparse nature of all matrices involved.
We employ two cross-validation techniques to estimate the hyper-parameters of
the inversion: the regularization parameter, the Moho density-contrast, and the
Normal Earth Moho depth.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Combining Bott's method, regularization, and tesseroids}

We propose a regularized version of Bott's method to invert gravity data for
estimating the depth of the Moho in spherical coordinates.
To adapt Bott's method to spherical coordinates,
we replace the right-rectangular prisms in the forward modeling
($\mathbf{d}(\mathbf{p}^k)$ in Eq.~\ref{eq:bott})
with tesseroids.
The tesseroid forward modeling uses the adaptive discretization algorithm
of \citet{uieda2016} to achieve accurate results.
Furthermore, our formulation maintains the regularized solution
for the Gauss-Newton method (Eq.~\ref{eq:gaussnewton-regul})
but replaces the full Jacobian matrix with the Bouguer plate approximation
(Eq.~\ref{eq:bott-gaussnewton}).
Here, the Jacobian matrix is a diagonal matrix whose elements are invariant
along successive iterations.
Using this approximation eliminates the cost of computing and storing
the full $N \times M$-dimensional Jacobian matrix $\mathbf{A}^k$ at each
iteration
(Eq.~\ref{eq:jacobian}).
Traditionally, the Jacobian matrix is computed using a first-order finite
difference scheme,
which requires $2 \times N \times M$ forward modeling operations per iteration.
Using Eq.~\ref{eq:bott-gaussnewton} requires $N$ multiplications that need only
be performed once.
This provides a considerable speed gain.

Matrix arithmetic operations can be performed efficiently by taking advantage
of the sparse nature of matrices $\mathbf{A}$ and $\mathbf{R}$
(respectively, Eq.~\ref{eq:bott-gaussnewton} and \ref{eq:regul}).
The same is true for solving the equation system in the Gauss-Newton method
(Eq.~\ref{eq:gaussnewton-regul}).
However, the computational cost of forward modeling is still present.
Particularly, forward modeling using tesseroids is more computationally
intensive than using right-rectangular prisms
because of the numerical integration and adaptive discretization
\citep{uieda2016}.
We show later in this article that sparse matrix multiplications and solving
the sparse linear system in Eq.~\ref{eq:gaussnewton-regul} account for less
than 0.1\% of the computation time required for a single inversion.

The main computational advantage of our formulation is that it retains the
efficiency of Bott's method while stabilizing the solution through the well
established formalism of Tikhonov regularization.

@@

We have developed a computationally efficient gravity inversion method in
spherical coordinates.
Our method extends the Gauss-Newton formulation of Bott's method
\citep{silva2014} to use tesseroids as model elements and Tikhonov
regularization.
The computational efficiency of our method is due to
using Bott's approximation for the Jacobian matrix
(Eq.~\ref{eq:bott-gaussnewton})
and using sparse matrix algorithms for arithmetic operations and the solution
of linear systems..
We employ two cross-validation techniques to estimate the hyper-parameters of
the inversion: the regularization parameter, the Moho density-contrast, and the
Normal Earth Moho depth.
